---
title: '`r ansp_admin$ANSP_short`'
categories:
  - metadata
  - ansp
type: ansp
slug: '`r ansp_admin$ANSP_short %>% str_to_lower() %>% str_replace_all(" ", "-")`'
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12,
  fig.height=8,
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  NULL)
options(encoding = 'UTF-8')

```

ANS Provider - `r ansp_admin$Country_Name`.


## Institutional Arrangements


## Status

`r ansp_main$Organisation`

* National Supervisory Authority (NSA): `r ansp_admin$NSA`

* Body responsible for:
  - Safety Regulation: `r ansp_admin$Saftey`
  - Airspace Regulation: `r ansp_admin$Airspace`
  - Economic Regulation: `r ansp_admin$Economic`
  


## Corporate Governance Structure (`r year_now`)




## `r ansp_admin$ANSP_short` (`r year_now`)
  



## Scope of Services (`r year_report`)

```{r services}

services_tbl <- tibble::tribble(
  ~Service, ~Provision,
  "GAT", service_gat,
  "OAT", service_oat,
  "Upper Airspace", service_uas,
  "Lower Airspace", service_las,
  "Oceanic, ANS", service_oce,
  "MET", service_met
)

x <- kable(services_tbl, format = "html", align = c("l", "r")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  column_spec(1, bold = FALSE, border_right = TRUE)

# HACK: remove table heading, from https://stackoverflow.com/a/44716658/963575
gsub("<thead>.*</thead>", "", x)
```



## Operational ATS Units (`r year_report`)

`r ansp_main$OPS_notes %>% str_replace_all("\r\n", "\r\n- ")`


## Key Financial and Operational Figures (ACE `r year_report`)

```{r key-figures}
key_figures_tbl <- tribble(
  ~what, ~amount,
  "Gate-to-gate total revenues (M EUR)"         , total_revenue,
  "Gate-to-gate total costs (M EUR)"            , total_cost,
  "Gate-to-gate ATM/CNS provision costs (M EUR)", provision_cost,
  "Gate-to-gate total ATM/CNS assets (M EUR)"   , total_assets,
  "Gate-to-gate ANS total capex (M EUR)"        , total_capex,
  "ATCO in OPS"                                 , staff_atco,
  "Gate-to-gate total staff (including MET staff^[if applicable])", staff_all,
  "Total IFR flight-hours controlled by ANSP ('000)", ifr_hours_controlled,
  "IFR airport movements controlled by ANSP ('000)" , apt_movements_controlled,
  "En-route sectors open at maximum configuration"  , ert_max_sectors,
  "Minutes of ATFM delays ('000)"                   , atfm_delays
)

x <- kable(key_figures_tbl, format = "html", align = c("l", "r")) %>% 
  kable_styling(full_width = FALSE,bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = FALSE, border_right = TRUE)

# HACK: remove table heading, from https://stackoverflow.com/a/44716658/963575
gsub("<thead>.*</thead>", "", x)
```


## Size (`r year_report`)

Size of controlled airspace: `r ansp_main$Total_airspace` $km^2$

```{r ansp-map}
knitr::include_graphics(str_c("../static/images/ansp/", generate_ansp_base_filename(ansp_shortname), ".png", collapse = ""))
```

